Phosphatidyl diazirine alkyne alcohol

### 2025-04-01 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Fixed the PDAA pages with the new dataset

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "Frank Stein"
    affiliations:
      - name: "Proteomics Core Facility, European Molecular Biology Laboratory"
        city: Heidelberg
        country: Germany
        postal-code: 69117
    orcid: 0000-0001-9695-1692
  - name: Jeremy M. Baskin
    affiliations:
      - name: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University"
        city: Ithaca
        state: NY
        postal-code: 14853
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, Frank Stein^2^, Jeremy M. Baskin^3^, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^3^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

@@

>>>>

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        department: Molecular Microbiology and Immunology
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "André Nadler"
    affiliations:
      - name: "Max Plank Institute"
        department: "Molecular Cell Biology and Genetics"
        city: Dresden
        country: Germany
        postal-code: 01307
    orcid: 0000-0001-6329-3910
  - name: "Frank Stein"
    affiliations:
      - name: "European Molecular Biology Laboratory"
        department: "Proteomics Core Facility"
        city: Heidelberg
        country: Germany
        postal-code: 69117
    orcid: 0000-0001-9695-1692
  - name: Jeremy M. Baskin
    affiliations:
      - name: "Cornell University"
        department: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology"
        city: Ithaca
        state: NY
        postal-code: 14853
    orcid: 0000-0003-2939-3138
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        department: "Chemical Physiology and Biochemistry"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        department: Molecular Microbiology and Immunology
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, André Nadler^2^, Frank Stein^3^, Jeremy M. Baskin^4^, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^3^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^4^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

@@

## Funding

This work was supported by funding from the National Institutes of Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM 127631 to C.S., and R01 GM151682 to JMB).

### 2025-04-01 IndividualStudies/WY_2021.qmd
Fixed the PDAA pages with the new dataset

```{r NewPlottingFunctions, include=FALSE, echo=FALSE}
RankedOrderPlotSpecial <- function(data) {
    ################
    #' A standardized Ranked Order plot theme
    #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
    ################

    # Applies ID column to each probe
    data <- data |>
      group_by(LipidProbe) |>
      arrange(logFC, .by_group = TRUE) |>
      mutate(ID = row_number()) |>
      ungroup()

    # First makes a ggplot template to later apply ggplotly
    RankedOrderPlots <- data |>
        ggplot(aes(x = ID,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Ranked-order gene") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12))  +
        theme(strip.text = element_text(
    size = 20))
    m <- list(l=50, r = 50, b= 100, pad = 4)

    RankedOrderPlotly <- ggplotly(RankedOrderPlots,
                            tooltip = c("text", dynamicTicks = TRUE),
                            hovermode = "closest",
                            autosize = T,
                            margin = m) |>
                    layout(showlegend = FALSE)

    return(RankedOrderPlotly)
}

MASpecial <- function(data) {

    ################
    #' A standardized MA plot function
    #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
    #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
    #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
    ################

    MAPlots <- data |>
        ggplot(aes(x = AveExpr,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n",
                                    "AveExpr: ", AveExpr, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 5))+
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Average Ion Intensity") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12)) +
        theme(strip.text = element_text(
    size = 20))

    m <- list(l=50, r = 50, b= 100, pad = 4)

    MAPlotly <- ggplotly(MAPlots,
                            tooltip = c("text", dynamicTicks = TRUE),
                            hovermode = "closest",
                            autosize = T,
                            margin = m) |>
                    layout(showlegend = FALSE)

    return(MAPlotly)
}

```{r HiddenDataWrangling, include=FALSE, echo=FALSE}

# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
#   filter(Coverage != 0 & Fold_change != 0) |>
#   mutate(gene_name = gene_name...3) |>
#   group_by(gene_name) |>
#   summarise(logFC = mean(log2(Fold_change)),
#             # pvalue = mean(pvalue),
#             numReplicates = n(),
#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
#   arrange(-logFC)

# median_logFC <- median(RawData$logFC)

# RawData$logFC <- RawData$logFC - median_logFC

# RawData <- RawData |> 
#   mutate(LipidProbe = "PDAA",
#         AveExpr = case_when(.default = AveExpr,
#                               AveExpr == -Inf ~ 0),
#                               hit_annotation = case_when(.default = "no hit",
#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
#   glimpse()

# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(biomaRt)
library(rentrez)

@@

@@

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

RankedOrderPlotSpecial(data)
```

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

MASpecial(data)
```

##### Venn Diagram

@@

###### Wrangling for the Venn Diagram ######
# Read the dataset

VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
  mutate(gene_name = gene_name...3)

# Separates out each of the genesets, then forces them back together in a vectorized list.
A_proteins <- VennData |>
  filter(Trial == 1) |>
  dplyr::select(gene_name)

B_proteins <- VennData |>
  filter(Trial == 2) |>
  dplyr::select(gene_name)

C_proteins <- VennData |>
  filter(Trial == 3) |>
  dplyr::select(gene_name)

VennList <- list("Trial 1" = as.list(A_proteins$gene_name), "Trial 2" = as.list(B_proteins$gene_name), "Trial 3" = as.list(C_proteins$gene_name))
```

```{r NAPE_Venn, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). A Venn diagram depicts the overlapping identification of proteins between the three trials (replicates)."

ggvenn <- ggvenn(VennList,
                      show_percentage = FALSE,
                      show_elements = FALSE,
                      fill_color = c("orange", "purple", "blue")) +
        labs(x = "", y = "") +
        theme_minimal()

ggvenn

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. logFC ratios are median normalized. \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified. As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01. \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),
                         rownames=FALSE)

>>>>

```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(limma)

@@

```{r WY_2025_seriousDataWrangling, include=FALSE, echo=FALSE}

# # RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))

# filtered_data <- RawData |> 
#   filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
#          if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
#   arrange(-Control_1)

# # Convert wide format to long format
# long_data <- filtered_data |> 
#   pivot_longer(cols = -gene_name, 
#                names_to = c("Condition", "Replicate"), 
#                names_sep = "_", 
#                values_to = "Abundance") |> 
#   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))

# # Count the number of observations per gene per condition
# complete_genes <- long_data |> 
#   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
#   group_by(gene_name, Condition) |> 
#   summarise(count = n(), .groups = "drop") |> 
#   pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
#   filter(Control == 3 & Sample == 3) |>  
#   pull(gene_name)

# # Filter the original dataset to include only these complete genes
# filtered_data <- long_data |> 
#   filter(gene_name %in% complete_genes)

# # Run t-test for each gene
# t_test_results <- filtered_data |> 
#   group_by(gene_name) |> 
#   summarise(
#     pvalue = t.test(Abundance[Condition == "Sample"], 
#                      Abundance[Condition == "Control"], 
#                      var.equal = TRUE)$p.value,
#     logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
#   ) |> 
#   mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
#           LipidProbe = "PDAA",
#           hit_annotation = case_when(.default = "no hit",
#                                       logFC > log2(1.5) &  pvalue < 0.05 ~ "enriched hit"))  # Adjust p-values for multiple testing

# averaged_data <- filtered_data |> 
#   group_by(gene_name) |>
#   summarise(AveExpr = log10(mean(Abundance)))

# data <- t_test_results |>
#   left_join(averaged_data)

# # write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

@@

##### Volcano plots

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are designated as not statistically significant. Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed."

VolcanoPlotStandardized(data)

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd).  Black proteins are designated as not statistically significant. Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed."

RankedOrderPlotStandard(data)
```

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd).  Black proteins are designated as not statistically significant. Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed."

MAStandard(data)
```

<!-- ##### Venn Diagram -->

@@

# ###### Wrangling for the Venn Diagram ######
# # Read the dataset

# VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))

# # Convert wide format to long format
# VennData <- VennData |> 
#   mutate(logFC_1 = log2(Sample_1 / Control_1),
#          logFC_2 = log2(Sample_2 / Control_2),
#          logFC_3 = log2(Sample_3 / Control_3)) |>
#   pivot_longer(cols = c(8,9,10)) |>
#   select(gene_name, name, value) |>
#   filter(!is.na(value)) |> 
#   mutate(Replicate = case_when(name == "logFC_1" ~ 1,
#                                name == "logFC_2" ~ 2,
#                                name == "logFC_3" ~ 3))

# # Separates out each of the genesets, then forces them back together in a vectorized list.
# A_proteins <- VennData |>
#   filter(Replicate == 1) |>
#   dplyr::select(gene_name)

# B_proteins <- VennData |>
#   filter(Replicate == 2) |>
#   dplyr::select(gene_name)

# C_proteins <- VennData |>
#   filter(Replicate == 3) |>
#   dplyr::select(gene_name)

# VennList <- list("Trial 1" = as.list(A_proteins$gene_name), "Trial 2" = as.list(B_proteins$gene_name), "Trial 3" = as.list(C_proteins$gene_name))
```

```{r NAPE_Venn, include=FALSE, echo=FALSE, warning=FALSE}
# #| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). A Venn diagram depicts the overlapping identification of proteins between the three trials (replicates)."

# ggvenn <- ggvenn(VennList,
#                       show_percentage = FALSE,
#                       show_elements = FALSE,
#                       fill_color = c("orange", "purple", "blue")) +
#         labs(x = "", y = "") +
#         theme_minimal()

# ggvenn

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed.",
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
                         rownames=FALSE)

### 2025-04-01 _site/LipidProbe/PhosphatidylAlcohol.qmd
Fixed the PDAA pages with the new dataset

```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(limma)

@@

```{r WY_2025_seriousDataWrangling, include=FALSE, echo=FALSE}

# # RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))

# filtered_data <- RawData |> 
#   filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
#          if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
#   arrange(-Control_1)

# # Convert wide format to long format
# long_data <- filtered_data |> 
#   pivot_longer(cols = -gene_name, 
#                names_to = c("Condition", "Replicate"), 
#                names_sep = "_", 
#                values_to = "Abundance") |> 
#   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))

# # Count the number of observations per gene per condition
# complete_genes <- long_data |> 
#   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
#   group_by(gene_name, Condition) |> 
#   summarise(count = n(), .groups = "drop") |> 
#   pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
#   filter(Control == 3 & Sample == 3) |>  
#   pull(gene_name)

# # Filter the original dataset to include only these complete genes
# filtered_data <- long_data |> 
#   filter(gene_name %in% complete_genes)

# # Run t-test for each gene
# t_test_results <- filtered_data |> 
#   group_by(gene_name) |> 
#   summarise(
#     pvalue = t.test(Abundance[Condition == "Sample"], 
#                      Abundance[Condition == "Control"], 
#                      var.equal = TRUE)$p.value,
#     logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
#   ) |> 
#   mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
#           LipidProbe = "PDAA",
#           hit_annotation = case_when(.default = "no hit",
#                                       logFC > log2(1.5) &  pvalue < 0.05 ~ "enriched hit"))  # Adjust p-values for multiple testing

# averaged_data <- filtered_data |> 
#   group_by(gene_name) |>
#   summarise(AveExpr = log10(mean(Abundance)))

# data <- t_test_results |>
#   left_join(averaged_data)

# # write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

## Data visualization

>>>>

```{r PDAA_setup, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(biomaRt)
library(rentrez)

@@

#### Data visualization
